---
title: "Impact of Marketing Investment on Customer Spending"
author: "Qingqing Yu"
format:
  html:
    theme: cosmo
  pdf: default
execute:
  echo: false
  warning: false
  message: false
---

```{r}
library(tidyverse)
library(readr)
library(ggplot2)
library(dplyr)
```

```{r}
market_data <- read_csv("assignment-1-creating-reproducible-reports-qyuu0033-design/data/35026278_Qingqing Yu.csv")
```

# Introduction

This report mainly focuses on the marketing strategies implemented by our company in the last quarter, such as advertising, email marketing, and coupons, and the marketing investment made. Based on the purchase records of customers, it examines whether higher marketing investment per customer has led to higher purchase amounts and whether there is a relationship between the two. The data mainly comes from the customer-level data of the last quarter.

# Research Question

This study mainly examines whether marketing investment can lead to higher customer purchasing power, and whether there is a certain relationship between the two. In essence, it is observing the relationship between total sales investment and customer purchasing power.

# Dataset Description

This dataset contains customer-level information regarding marketing activities and purchasing behaviors. It includes variables such as advertising expenses, email engagement, coupon usage, and total purchase amount. These data represent the marketing activity situation of a certain quarter. This dataset has been cleaned, with missing values removed, and all numerical variables have been correctly formatted. Duplicate records (if any) have been checked and deleted. Additionally, to enhance clarity and consistency, the variables have been renamed.
```{r}
glimpse(market_data)
summary(market_data)
```

I have figured out what each column of the data represents. Among them, I consider the "customer id" and "notes" columns to be unnecessary, so the "NA" values that appear in the "notes" column can be ignored.

The dataset contained missing values in the purchase amount variable. These observations were removed to ensure the accuracy of the analysis. The proportion of missing data was relatively small and did not significantly impact the overall dataset.
```{r}
drop_na_data <- market_data %>%
  drop_na(purchase_amount)
```